Plots for Latent Hawkes Paper

### 2021-05-18 output_scripts/Paper_Plots.Rmd
start rmd for revisions

mtext(text=expert_rank_10[[current_cohort]], side=1, line=1.8, outer=TRUE, cex=1.8,
      at=1/14*c(1:12)-1/22)
mtext(text = expert_rank_10[[current_cohort]],
      side = 2, line = 0.5, outer = TRUE, cex = 1.8,
      at =1/12*c(12:1)-1/20, las = 2)
mtext(text = "(b)", side = 3, line = 1.4, outer = TRUE,
      cex = 2.2,
      at=0.45, font=2)
#dev.off()
```

@@

    if(m==3){
      text(text.x.adj[j],text.y[j],text.x[j],cex=2.4)
    }
  }
  ## bottom
  mtext(text=expression(f[1],f[2],f[3],f[4],f[5]), side=1, line=2.4, outer=TRUE, 
        at=c(1:length(object_par$f_vec_1))/length(object_par$f_vec_1)-0.1,
        cex=2)
  mtext(text="Latent rank variables", side=1, line=5.3, outer=TRUE, cex=2.25,
        at=0.5)
  ## top
  mtext(text="(a)", side=3, line=0, outer=TRUE, cex=2.5,
        at=0.5, font=2)
  ## left
  mtext(text=rev(c("C-HP  ","C-DCHP","C-MMHP")), side=2, line=0.5, outer=TRUE, 
        at=c(0:2)/3+0.15,
        cex=1.75, las=2)
}

>>>>

mtext(text=expert_rank_10[[current_cohort]],
      side = 1, line = 1.8, outer = TRUE, cex = 1.8,
      at=1/14*c(1:12)-1/22)
mtext(text = expert_rank_10[[current_cohort]],
      side = 2, line = 0.5, outer = TRUE, cex = 1.8,
      at =1/12*c(12:1)-1/20, las = 2)
mtext(text = "(b)", side = 3, line = 1.4, outer = TRUE,
      cex = 2.2,
      at=0.45, font=2)
#dev.off()
```

@@

    if(m==3){
      text(text.x.adj[j],text.y[j],text.x[j],cex=2.4)
    }
  }
  ## bottom
  mtext(text = expression(f[1],f[2],f[3],f[4],f[5]), 
        side = 1, line = 2.4, outer = TRUE, 
        at = c(1:length(object_par$f_vec_1))/length(object_par$f_vec_1)-0.1,
        cex = 2)
  mtext(text = "Latent rank variables", side = 1,
        line = 5.3,
        outer = TRUE,
        cex = 2.25,
        at = 0.5)
  ## top
  mtext(text = "(a)", side = 3,
        line = 0, 
        outer = TRUE,
        cex = 2.5,
        at = 0.5, font = 2)
  ## left
  mtext(text=rev(c("C-HP  ","C-DCHP","C-MMHP")), side=2, line=0.5, outer=TRUE, 
        at=c(0:2)/3+0.15,
        cex=1.75, las=2)
}
